An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-24 VLDB2026/main.tex
Update main.tex

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
		\caption{Effect of attribute distribution on query performance (single thread)}
		\label{fig:exp_3_1}
	\end{figure*}

	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios. To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries. \textcolor{orange}{In this experiment, we only evaluate the algorithms that support this query scenario.}
	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios. To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.

>>>>

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
		\caption{Effect of attribute distribution on query performance (single thread)}
		\label{fig:exp_3_1}

		\footnotesize{
		\begin{center}
			\begin{minipage}{\linewidth}
				\centering	
				Note: \textit{Strong} represents robust to attribute distribution, \textit{Weak} represents sensitive to attribute distribution 
			\end{minipage}
		\end{center}
		}
	\end{figure*}

	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios. To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries. \textcolor{orange}{Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND. Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments.}
	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios. To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.
